Binning Strategies and Related Loss for Large Data

### 2015-04-24 Paper.Rnw
Adjust language about reduced binned data sizes for consistency  (data triples, not observations)

\begin{figure}[hbtp]
%  \begin{minipage}{.31\linewidth}
% <<noFreqBin, echo=FALSE, out.width='.8\\linewidth',fig.width=4, fig.height=4>>=
% binout1 <- RectBin2d(datlist[[2]]$x,datlist[[2]]$y,0,0,5,5,type="standard")
% qplot(binxs, binys, geom="tile", fill=binfreq, data=binout1[[1]],
%             main="No Freq Binning") +
%   xlab("") + ylab("")+
%   scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43",
%                       guide = guide_colourbar(label.position="bottom", label.hjust=0.5,  
%                                            title.position = "top")) + 
%   theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
%                      panel.grid= element_blank(),
%                      plot.margin = unit(c(.1,.1,.1,.1),"cm") )
% @
%  \end{minipage}
%\hfil\begin{minipage}{.685\linewidth}
<<FreqBinPlots, echo=FALSE, out.width='\\linewidth',fig.width=10, fig.height=5>>=
binout1 <- RectBin2d(datlist[[2]]$x,datlist[[2]]$y,0,0,5,5,type="standard")
freqgrps = 5
binoutFreqGroups <- freqBin(binout1, binType="standard", ncolor=freqgrps, logCount=FALSE)
binoutQuantFreqGroups <- freqBin(binout1, binType="quantile", ncolor=freqgrps, logCount=FALSE)
binoutLogFreqGroups <- freqBin(binout1, binType="standard", ncolor=freqgrps, logCount=TRUE)
binoutQuantLogFreqGroups <- freqBin(binout1, binType="quantile", ncolor=freqgrps, logCount=TRUE)
cols <- seq_gradient_pal(low="#56B1F7", high="#132B43", space="Lab")((0:freqgrps)/freqgrps)

@@

Figure~\ref{airline5mins-binning} displays the binned scatterplots for the flight departure data with larger bins. Binning data by five-minute intervals produces a more high-level summary of the relationship between actual and scheduled departure time, though it necessarily obscures some of the finer details. In addition, binning data by five minute intervals reduces the size of the data set to a much more manageable 19,787 observations  which can be easily manipulated on probably any modern computer. Binning by 15-minute intervals reduces the data set to a nearly-trivial 3,575 observations, but the graphical summary becomes granular and less appealing at that resolution.

>>>>

\begin{figure}[hbtp]
%  \begin{minipage}{.31\linewidth}
% <<noFreqBin, echo=FALSE, out.width='.8\\linewidth',fig.width=4, fig.height=4>>=
% binout1 <- RectBin2d(datlist[[2]]$x,datlist[[2]]$y,0,0,5,5,type="standard")
% qplot(binxs, binys, geom="tile", fill=binfreq, data=binout1[[1]],
%             main="No Freq Binning") +
%   xlab("") + ylab("")+
%   scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43",
%                       guide = guide_colourbar(label.position="bottom", label.hjust=0.5,  
%                                            title.position = "top")) + 
%   theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
%                      panel.grid= element_blank(),
%                      plot.margin = unit(c(.1,.1,.1,.1),"cm") )
% @
%  \end{minipage}
%\hfil\begin{minipage}{.685\linewidth}
<<FreqBinPlots, echo=FALSE, out.width='\\linewidth',fig.width=10, fig.height=4.8>>=
binout1 <- RectBin2d(datlist[[2]]$x,datlist[[2]]$y,0,0,5,5,type="standard")
freqgrps = 5
binoutFreqGroups <- freqBin(binout1, binType="standard", ncolor=freqgrps, logCount=FALSE)
binoutQuantFreqGroups <- freqBin(binout1, binType="quantile", ncolor=freqgrps, logCount=FALSE)
binoutLogFreqGroups <- freqBin(binout1, binType="standard", ncolor=freqgrps, logCount=TRUE)
binoutQuantLogFreqGroups <- freqBin(binout1, binType="quantile", ncolor=freqgrps, logCount=TRUE)
cols <- seq_gradient_pal(low="#56B1F7", high="#132B43", space="Lab")((0:freqgrps)/freqgrps)

@@

Figure~\ref{airline5mins-binning} displays the binned scatterplots for the flight departure data with larger bins. Binning data by five-minute intervals produces a more high-level summary of the relationship between actual and scheduled departure time, though it necessarily obscures some of the finer details. In addition, binning data by five minute intervals reduces the size of the data set to a much more manageable 19,787 reduced binned data triples, which can be easily manipulated on probably any modern computer. Binning by 15-minute intervals reduces the data set to a nearly-trivial 3,575 reduced binned data triples, but the graphical summary becomes granular and less appealing at that resolution.
